\Huge \textcolor{titleTextColor}{ \textsf{\textbf{ \fontsize{85}{60}\selectfont How innovations thrive in GRASS GIS }} }

### 2017-02-21 grassposter/2017_NCGIS_How_innovations_thrive/poster.tex
rearrange, add background
git-svn-id: https://svn.osgeo.org/grass/grass-promo@70650 15284696-431f-4ddb-bdfa-cd5b030d7da7

\definecolor{titleTextColor}{HTML}{009000}
\definecolorpalette{grassColorPalette} {
  \definecolor{colorOne}{HTML}{419041}
}
\usecolorstyle[colorPalette=grassColorPalette]{Britain}

@@

\renewcommand{\labelitemi}{\textcolor{gray}{$\bullet$}\hspace{0.5ex}}

Poster topic highlights:

@@

General GRASS GIS highlights:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Spatio-Temporal Data Analysis}}{
The time dimension was introduced in GRASS GIS version 7 for vector maps, rasters, and 3D rasters
which transformed GRASS GIS into a fully-featured temporal GIS \citep{Gebbert20141, gebbert2015grass}.
Time series of map layers are managed in space time datasets, a new data type in GRASS GIS,
and are still accessible also as individual map layers.
Based on the GRASS GIS Temporal Framework Python application programming interface (API),
more than 50 modules were implemented to manage, analyze, process
and visualize space time datasets.
More than 100,000 map layers can be now handled efficiently in GRASS GIS.
Example usages of this functionality include
analysis of the
European Climate Assessment \& Dataset ECA\&D \citep{Haylock2008_climate_series}
and temperate climate zone in the European Union identification \citep{Gebbert20141}.

% \vspace*{1cm}

\medskip
Landuse classes and derived landscape diversity according to Shannon index in near Charlotte (NC, USA)
% r.diversity input=development_2006 prefix=diversity alpha=0.5 size=65
% r.li.shannon input="development_2006" config="conf_diversity_65.0" output="diversity_shannon_size_65.0"
}

GRASS GIS entails several modules that constitute the result of active research on natural hazards.
The \gmodule{r.sim.water} simulation model (Mitas and Mitasova, 1998 \cite{Mitas1998b})
for overland flow with spatially variable rainfall excess conditions was integrated into the Emergency
Routing Decision Planning system as a WPS (Raghavan et al., 2014 \cite{raghavan2014deploying}).
The module \gmodule{r.sim.water} together with
the module \gmodule{r.sim.sediment} for erosion-deposition modeling
implements a path sampling algorithm which is robust and easy to parallelize.
A unique least cost path algorithm which doesn't need any depression filling
was implemented in \gmodule{r.watershed} module in 1989
and it was updated for massive data sets in 2011.
% TODO: refs
The \gmodule{r.sim.water} module was also utilized by Petrasova et al., 2014 \cite{Petrasova2014} and is now part of
\emph{Tangible Landscape}, a tangible GIS system, which also incorporated \gmodule{r.damflood},
a dam break inundation simulation \cite{cannata2012two}.

\centering
\begin{minipage}{0.65\linewidth}
\centering
\includegraphics[width=0.5\textwidth]{rsimwater_architects}
\\
Overland flow simulated by \gmodule{r.sim.water} used for landscape
architecture design in Tangible Landscape environment
(Historical master plan for Lake Raleigh, NC, USA)
\end{minipage}
~
\begin{minipage}{0.5\linewidth}
% TODO: damflood on Lake Raleigh
% \includegraphics[width=\textwidth]{damflood_tangible}
% Coal ash pond breach in Tangible Landscape environment using \gamodule{r.damflood} module
\end{minipage}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Image Segmentations}}{
\gamodule{r.smooth.seg} (formerly \gmodulenolink{r.seg})
was created by Alfonso Vitti \citep{vitti2008free, vitti2012mumford}
and implemented a piece-wise smooth approximation of the original image
according to \cite{mumford1989optimal} and \cite{march1997variational}
which can be used to reduce noise in the original image.
This supplemented \gmodule{r.clump} available from 1980s
which groups pixes with same categories (or integer values).
The latest version of \gmodule{r.clump} coming in GRASS GIS 7.4
supports multiple image bands (or any rasters maps) as input.
Clumping of cells based on threshold value and clumping
of double precision floating point input is supported as well in the new version.

\vspace*{0.6cm}

% + vector algebra
An experimental module \gamodule{v.feature.algebra} (formerly \gmodulenolink{v.mapcalc}) from 2002
% actually, the original by Radim Blazek (Jun 11, 2002) seems to be more similar to the current v.mapcalc
% it was using Vect_overlay_str_to_operator Vect_overlay
% it was replaced by code by Christoph Simon in Aug 7, 2002
was replaced by Python for GRASS GIS C libraries (PyGRASS) in GRASS GIS 7.0.
However, new \gamodule{v.mapcalc} module is available with richer syntax and functionality.

\centering
\begin{minipage}{0.9\linewidth}
\begin{center}
\includegraphics[width=.3\textwidth]{topo_original}
~
\includegraphics[width=.3\textwidth]{topo_errors}
~
\includegraphics[width=.3\textwidth]{topo_fixed}
Original vector imported without cleaning (left),
identified errors (middle),
automatically topologically corrected vector (right)
\end{center}
\end{minipage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Vector Network Analysis}}{
In 2003 Radim Blazek introduced shortest path analysis (\gmodule{v.net.path}),
traveling salesman (\gmodule{v.net.salesman}),
and several other modules for vector network analysis (staring with \gmodule{v.net}).
Over the years, the number of available algorithms increased to over 15 modules
including for example, centrality measures and connected components added in 2009 by Daniel Bundala.
In 2014 Stepan Turek implemented turns support into all relevant vector network modules.
Also since GRASS GIS 7.0 all vector network analysis tools provide fine control over node costs.

@@

@@

>>>>

\definecolor{textcolor}{HTML}{000000}

\definecolor{titleTextColor}{HTML}{009000}
\definecolorpalette{grassColorPalette} {
  \definecolor{colorOne}{HTML}{419041}
  % \definecolor{colorTwo}{HTML}{cccccc}
  \definecolor{colorTwo}{HTML}{dddddd}
  \definecolor{colorThree}{HTML}{F1B52D}
  % \definecolor{colorThree}{HTML}{EFA126}
}

\usetheme{Rays}
\usecolorstyle[colorPalette=grassColorPalette]{Britain}

@@

\renewcommand{\labelitemi}{\textcolor{gray}{$\bullet$}\hspace{0.5ex}}
\newcommand{\blocksectiontitle}[1]{\bigskip\textbf{\textcolor{gray}{\textsf{#1}}}}

\blocksectiontitle{Poster topic highlights}

@@

\blocksectiontitle{General GRASS GIS highlights}

@@

@@

@@

\begin{minipage}{\listlogowidth}
\centering
\includegraphics[width=0.5\linewidth]{grass}
\end{minipage}
\listhspace
\begin{minipage}{\listtextwidth}
We acknowledge all members of the GRASS GIS community both users and developers.
Specifically we
\end{minipage}

@@

GRASS GIS entails several modules that constitute the result of active research on natural hazards.
The \gmodule{r.sim.water} simulation model \citep{Mitas1998b}.
for overland flow with spatially variable rainfall excess conditions was integrated into the Emergency
Routing Decision Planning system as a WPS (Raghavan et al., 2014 \cite{raghavan2014deploying}).
The module \gmodule{r.sim.water} together with
the module \gmodule{r.sim.sediment} for erosion-deposition modeling
implements a path sampling algorithm which is robust and easy to parallelize.
A unique least cost path algorithm which doesn't need any depression filling
was implemented in \gmodule{r.watershed} module in 1989
and it was updated for massive data sets in 2011.
% TODO: refs
The \gmodule{r.sim.water} module was also utilized by \cite{Petrasova2014} and is now part of
\emph{Tangible Landscape}, a tangible GIS system, which also incorporated \gmodule{r.damflood},
a dam break inundation simulation \citep{cannata2012two}.

\centering

\begin{minipage}{0.49\linewidth}
\centering
\includegraphics[width=0.7\textwidth]{rsimwater_architects}
\end{minipage}
~
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\textwidth]{damflood_tangible}
\end{minipage}

\begin{minipage}{0.49\linewidth}
\centering
Overland flow simulated by \gmodule{r.sim.water} used for landscape
architecture design in Tangible Landscape environment
(Historical master plan for Lake Raleigh, NC, USA)
\end{minipage}
~
\begin{minipage}{0.49\linewidth}
Dam breach on Lake Raleigh (NC, USA) in Tangible Landscape environment simulated using \gamodule{r.damflood} module
\end{minipage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Image Segmentations}}{
\gamodule{r.smooth.seg} (formerly \gmodulenolink{r.seg})
was created by Alfonso Vitti \citep{vitti2008free, vitti2012mumford}
and implemented a piece-wise smooth approximation of the original image
according to \cite{mumford1989optimal} and \cite{march1997variational}
which can be used to reduce noise in the original image.

This supplemented \gmodule{r.clump} available from 1980s
which groups pixes with same categories (or integer values).
The latest version of \gmodule{r.clump} coming in GRASS GIS 7.4
supports multiple image bands (or any rasters maps) as input.
Clumping of cells based on threshold value and clumping
of double precision floating point input is supported as well in the new version.

\vspace*{0.7cm}

\begin{center}
\begin{minipage}{0.9\linewidth}
\begin{center}
\includegraphics[width=.3\textwidth]{topo_original}
~
\includegraphics[width=.3\textwidth]{topo_errors}
~
\includegraphics[width=.3\textwidth]{topo_fixed}
Original vector imported without cleaning (left),
identified errors (middle),
automatically topologically corrected vector (right)
\end{center}
\end{minipage}
\end{center}

An experimental module \gamodule{v.feature.algebra} (formerly \gmodulenolink{v.mapcalc}) from 2002
% actually, the original by Radim Blazek (Jun 11, 2002) seems to be more similar to the current v.mapcalc
% it was using Vect_overlay_str_to_operator Vect_overlay
% it was replaced by code by Christoph Simon in Aug 7, 2002
was replaced by Python for GRASS GIS C libraries (PyGRASS) in GRASS GIS 7.0.
However, new \gamodule{v.mapcalc} module is available with richer syntax and functionality.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Spatio-Temporal Data Analysis}}{
The time dimension was introduced in GRASS GIS version 7 for vector maps, rasters, and 3D rasters
which transformed GRASS GIS into a fully-featured temporal GIS \citep{Gebbert20141, gebbert2015grass}.
Time series of map layers are managed in space time datasets, a new data type in GRASS GIS,
and are still accessible also as individual map layers.
Based on the GRASS GIS Temporal Framework Python application programming interface (API),
more than 50 modules were implemented to manage, analyze, process
and visualize space time datasets.
More than 100,000 map layers can be now handled efficiently in GRASS GIS.
%
Example usages of this functionality include
analysis of the
European Climate Assessment \& Dataset ECA\&D \citep{Haylock2008_climate_series}
and temperate climate zone in the European Union identification \citep{Gebbert20141}.

\vspace*{1.5cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Vector Network Analysis}}{
In 2003 Radim Blazek introduced shortest path analysis (\gmodule{v.net.path}),
traveling salesman (\gmodule{v.net.salesman}),
and several other modules for vector network analysis (staring with \gmodule{v.net}).
Over the years, the number of available algorithms increased to over 15 modules
including for example, centrality measures and connected components added in 2009 by Daniel Bundala.
In 2014 Stepan Turek implemented turns support into all relevant vector network modules.
Also since GRASS GIS 7.0 all vector network analysis tools provide fine control over node costs.
% combination with r.cost/r.walk workflows \citep{Petrasova2014}

\vspace*{0.5cm}

\vspace*{1ex}

Landuse classes and derived landscape diversity according to Shannon index in near Charlotte (NC, USA)
% r.diversity input=development_2006 prefix=diversity alpha=0.5 size=65
% r.li.shannon input="development_2006" config="conf_diversity_65.0" output="diversity_shannon_size_65.0"
}
